Comments on Blair and Sambanis, 2020, \"Forecasting Civil Wars: Theory and Structure in an Age of 'Big Data' and Machine Learning\", *JCR*

### 2020-06-06 paper.Rmd
fix fallback bib path

---
title: "Comments on Blair and Sambanis, 2020, \"Forecasting Civil Wars: Theory and Structure in an Age of 'Big Data' and Machine Learning\", *JCR*"
author: Andreas Beger and Richard K. Morgan and Michael D. Ward
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  pdf_document:
    keep_tex: true
references:
- id: blair2020forecasting
  title: "Forecasting Civil Wars: Theory and Structure in an Age of 'Big Data' and Machine Learning"
  author:
  - family: Blair
    given: Robert A.
  - family: Sambanis
    given: Nicholas
  container-title: Journal of Conflict Resolution
  type: article-journal
  issued:
    year: 2020
bibliography: 
  - "`r user <- Sys.info()[['user']]; if (user=='andybega')  '/Users/andybega/Work/whistle/master.bib' else if (user=='mdw') '/Users/mdw/Git/whistle/master.bib' else references.bib`"
---

>>>>

---
title: "Comments on Blair and Sambanis, 2020, \"Forecasting Civil Wars: Theory and Structure in an Age of 'Big Data' and Machine Learning\", *JCR*"
author: Andreas Beger and Richard K. Morgan and Michael D. Ward
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  pdf_document:
    keep_tex: true
references:
- id: blair2020forecasting
  title: "Forecasting Civil Wars: Theory and Structure in an Age of 'Big Data' and Machine Learning"
  author:
  - family: Blair
    given: Robert A.
  - family: Sambanis
    given: Nicholas
  container-title: Journal of Conflict Resolution
  type: article-journal
  issued:
    year: 2020
bibliography: 
  - "`r user <- Sys.info()[['user']]; if (user=='andybega')  '/Users/andybega/Work/whistle/master.bib' else if (user=='mdw') '/Users/mdw/Git/whistle/master.bib' else 'references.bib'`"
---
